Creative Destruction

### 2016-03-18 paper.tex
added sources
asdf

\section{Creative Destruction in the Theory of Technological Evolution}
The aim of this section to situate creative destruction in the theory of technological evolution.
Many authors have different ideas of technological evolution; however, the important component for this discussion is that there is some selection process by which fit technologies remain relevant to society.
The aim of the selection process is an open question.
Economists like Jaffe believe that technologies are selected because of their potential usage for economic profits \cite{jaffe}.
Social constructivists believe that technologies are selected because of a complex causal web involving society, social conventions, economics, history, psychology and so on \cite{scot}.
For our treatment of technological evolution, we do not believe it be too important how selection, but rather, it is important that selection occurs. 
With this in mind, we use Brian Arthur's simple explanation of selection: a technology is useful to humans \cite{arthur}.
We say that a particular technology has a use-value corresponding to how useful the technology is to society, humans, or the economy.

@@

Creative destruction is concerned with the third case: where a new technology $u$ reduces the use-value of an old technology $t$. 
Biologists identify a similar process to creative destruction occurring in the selection of species. 
The phenomenon is called \textit{competitive exclusion}. 
Competitive exclusion is the idea that if two species are competing for the same resource, then one of the species will overcome the other, forcing the other species to adapt or die \cite{wiki-competitive-exclusion}. 
In recent years, observational, experimental and simulation-based evidence has surfaced to cause Biologists to question the simplicity of competitive exclusion.
We did not examine the new evidence close enough to explain here.

@@

If use-value and reproductive success are not highly correlated, then there are a number of steps one could take.
First, one could use reproductive success instead of use-value when describing selection and creative destruction. 
The theory would likely hold, but there many be detailed differences. 
Second, one could use this as support than technological evolution is not darwinian: the important factor in technological evolution is not reproduction but rather the use-value of a technology
\footnote{This is an interesting idea. Reproductive power may not be a central component of evolutionary systems.}.

\subsection{Implications on the Theory of Technology}
\section{Philosophical Considerations of Creative Destruction}

>>>>

\section{Creative Destruction in the Theory of Technological Evolution}
The aim of this section to situate creative destruction in the theory of technological evolution.
Many authors have different ideas of technological evolution; however, the important component for this discussion is that there is some selection process by which fit technologies remain relevant to society.
The aim of the selection process is an open question.
Economists like Jaffe believe that technologies are selected because of their potential for economic profits \cite{jaffe}.
Social constructivists believe that technologies are selected because of a complex causal web involving society, social conventions, economics, history, psychology and so on \cite{scot}.
For our treatment of technological evolution, we do not believe it be too important how selection, but rather, it is important that selection occurs. 
With this in mind, we use Brian Arthur's simple explanation of selection: a technology is useful to humans \cite{arthur}.
We say that a particular technology has a use-value corresponding to how useful the technology is to society, humans, or the economy.

@@

Creative destruction is concerned with the third case: where a new technology $u$ reduces the use-value of an old technology $t$. 
Biologists identify a similar process to creative destruction occurring in the selection of species. 
The phenomenon is called \textit{competitive exclusion}. 
Competitive exclusion is the idea that if two species are competing for the same resource, then one of the species will overcome the other, forcing the other species to adapt or die \cite{wiki}. 
In recent years, observational, experimental and simulation-based evidence has surfaced to cause Biologists to question the simplicity of competitive exclusion.
We did not examine the new evidence close enough to explain here.

@@

If use-value and reproductive success are not highly correlated, then there are a number of steps one could take.
First, one could use reproductive success instead of use-value when describing selection and creative destruction. 
The theory would likely hold, but there many be detailed differences. 
Second, one could use this as support that technological evolution is not darwinian: the important factor in technological evolution is not reproduction but rather the use-value of a technology
\footnote{This is an interesting idea. Reproductive power may not be a central component of evolutionary systems.}.

\subsection{Implications on the Theory of Technology}
This section discusses the implications of creative destruction on the theory of technology.

The first implication of creative destruction is that faster invention creation results in faster destruction.
The idea is that as society innovates more, creates new inventions, then there is simultaneously a destruction of old technology. 
And since society is innovating more, presubly there is more destruction.
There may be a net-effect of more innovation, but it is important that destruction may increase in periods of rapid innovation.
This suggests that technology is subject a phenomenon like Newton's third law: the more technology there is, the greater the push-back on old technology.

The second implication of creative destruction is that there could be a net-decrease in technology. 
The idea of creative destruction leaves open the possibility that more technologies are destroyed than are created.
That being said, as far as we are aware, a net-decrease in technology has not been observed.
Yet this is an idea that worred Marx and Schumpeter, albeit their concern was with capitalism not technology.
Marx and Schumpeter worried that capitalism would destroy itself; there would be so much sudden growth destroying the old system, and the system would collapse.

We find it imaginable that a new series of technology destroy old technology too quickly, rendering the new and old technology useless.
Consider many sudden innovations to the internet.
The internet is a highly complex, abstract, layered, decentralized web of interactions on which much technology relies.
One could imagine that we, society, decide to improve the internet, but improve it such that the old infrastructure is destroyed and the new infrastructure insufficient or incomplete.
We, society, have buried ourselves into a hole.
We, society, don't have reliable technology to use. 
We can't simply reimplement the old internet because it is too intertwined, too complicated.
And we can't use the new internet for whatever reason.
In the end, more was destroyed than created.

\section{Philosophical Considerations of Creative Destruction}
This section discusses philosophical considerations of creative destruction.
We outline three philosphical implications.

First, creative destruction makes technology more unpredictable.
The reason for this hearkens back to Brian Arthur's idea of primitives. 
Arthur reasons that new technology is the product of a new combination of primitives. 
Creative destruction

\bibliographystyle{apalike}
\bibliography{paper}
